\sysfull

### 2018-04-15 paper/evaluation.tex
added intro paragraph about manual code transform by alpaca

\textcolor{red}{highlight the difference between Alpaca GCC and Alpaca Clang. Alpaca GCC is about 30\%-40\% faster than Alpaca Clang. Writing Alpaca program by hand is a very trick thing and it is very error prone. Reason: a programmer needs to identify the write-after-read dependencies, change variables' names, and modify instructions accordingly, in general writing Alpaca code by hand is not a recommended, for that a compiler is needed}

@@

Our aim is to assess \sys as detailed as possible. For this we have characterized \sys runtime performance (execution time) considering task adaptation: task coalescing and downscaling. We also characterize \sys overhead showing precisely what is the source of \sys superior performance. Additionally, we characterize \sys code.

>>>>

%\textcolor{red}{highlight the difference between Alpaca GCC and Alpaca Clang. Alpaca GCC is about 30\%-40\% faster than Alpaca Clang. Writing Alpaca program by hand is a very trick thing and it is very error prone. Reason: a programmer needs to identify the write-after-read dependencies, change variables' names, and modify instructions accordingly, in general writing Alpaca code by hand is not a recommended, for that a compiler is needed}

@@

Our aim is to assess \sys as detailed as possible. For this we have characterized \sys runtime performance (execution time), based on a set of benchmarks, considering task adaptation: task coalescing and downscaling. We also characterize \sys overhead showing precisely what is the source of \sys superior performance. Additionally, we characterize \sys code.

\sys is compared to Alpaca runtime. We remind the reader that the benchmarks for Alpaca were hand-transformed in a time-consuming manual process from Clang (LLVM-generated code) to GCC. The manual code transformation was required as \sys was written with GCC in mind, and Alpaca cannot support any other complier than LLVM.
